---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(haven)
library(readxl)
theme_set(theme_light())

full_data <- read_dta("ji_and_jiang_2019/data.dta")
read_dta("ji_and_jiang_2019/abs3_merge_party.dta")
read_dta("ji_and_jiang_2019/abs4_merge_party.dta")
```



```{r}
full_data %>% 
  count(survey, sort = T)
```

######################################################################################
# Figure 1 Sample Deviation from Population Statistics: Before and After Reweighting #
######################################################################################

```{r}
data_1 <- read_excel("ji_and_jiang_2019/Fig.xlsx", sheet = 1)

datatidyr <- data_1 %>% gather(attribute, value, CCP:age) %>% 
  mutate(att = factor(attribute, levels = c("CCP", "female", "edu", "age"),
                      labels=c("% CCP membership","% of female CCP member","% of college educated CCP member","% of CCP member at age<=35"))) %>% 
  mutate(survey1 = factor(survey, levels = c("ABS4(2015)", "ABS3(2011)", "CGSS2015", "CGSS2013","CGSS2012","CGSS2010","CFPS2014")))

pdf("Figure1.pdf",width=10, height=4)

datatidyr %>% 
  ggplot(aes(x = value, y = att, group = as.factor(group),
                     shape = as.factor(group), color = as.factor(group))) + 
  geom_point(size = 2) + 
  facet_grid(. ~ survey1) + 
  scale_y_discrete(limits = c("% of CCP member at age<=35","% of college educated CCP member",
                            "% of female CCP member","% CCP membership")) +
  geom_vline(aes(xintercept=0), colour="#62BCE9", linetype="dashed") +
  scale_color_brewer(palette="Set1",
                     name = "",
                     breaks=c("Origin", "Raked"),
                     labels=c("Before weight calibration","After weight calibration")) +
  scale_shape_manual(name = "",
                     breaks=c("Origin", "Raked"),values=c(19,17),
                     labels=c("Before weight calibration","After weight calibration")) +
  xlab("% in Survey - % in Population")+ylab("")+
  scale_x_continuous(limits=c(-0.22,0.1),labels = scales::percent_format(accuracy = 1)) +
  theme_bw() + 
  theme(axis.text.x = element_text(size=8),
        axis.text.y = element_text(size=11),
        axis.title.x=element_text(face="bold",vjust=-.5,size=11),
        axis.title.y=element_text(face="bold",vjust=1),
        legend.text = element_text(size=11),
        strip.text=element_text(size=13),
        text=element_text(family="Times"),
        legend.position="bottom",
        legend.direction="horizontal")

dev.off() 
```


#######################################################
# Figure 2: Main Result: Weighted Difference in Means #
#######################################################


```{r}
library(ggridges)

data_2 <- read_dta("ji_and_jiang_2019/data.dta")

datatidyr_2 <- data_2 %>% 
  gather(attribute, value, social_value:modern_all_value) %>% 
  mutate(values = factor(attribute, levels = c("social_value", "political_value", "intl_value", "modern_all_value"),
                         labels = c("Social","Political","International","Overall modern value")))

dg_cfps    <- data.frame(values = unique(datatidyr_2$values),
                         labels1 = c("Public:0.093\n[0.082,0.104]","","",""),
                         labels2 = c("CCP:0.410\n[0.373,0.447]","","",""))

dg_cgss2010 <- data.frame(values = unique(datatidyr_2$values),
                          labels1 = c("Public:-0.090\n[-0.109,-0.071]","","",""),
                          labels2 = c("CCP:0.337\n[0.287,0.386]","","",""))

dg_cgss2012 <- data.frame(values = unique(datatidyr_2$values),
                          labels1 = c("Public:-0.050\n[-0.069,-0.031]","","",""),
                          labels2 = c("CCP:0.412\n[0.360,0.463]","","",""))

dg_cgss2013 <- data.frame(values = unique(datatidyr_2$values),
                          labels1 = c("Public:-0.031\n[-0.050,-0.012]","","",""),
                          labels2 = c("CCP:0.301\n[0.243,0.360]","","",""))

dg_cgss2015 <- data.frame(values = unique(datatidyr_2$values),
                          labels1 = c("Public:-0.054\n[-0.074,-0.035]","","",""),
                          labels2 = c("CCP:0.287\n[0.229,0.345]","","",""))

dg_abs3 <- data.frame(values = unique(datatidyr_2$values),
                    labels1 = c("Public:0.012\n[-0.025,0.048]",
                              "Public:0.012\n[-0.025,0.048]",
                              "Public:0.005\n[-0.031,0.041]",
                              "Public:0.012\n[-0.024,0.048]"),
                    labels2 = c("CCP:0.230\n[0.150,0.310]",
                              "CCP:0.326\n[0.244,0.407]",
                              "CCP:0.169\n[0.084,0.254]",
                              "CCP:0.347\n[0.265,0.429]"))

dg_abs4 <- data.frame(values = unique(datatidyr_2$values),
                    labels1 = c("Public:0.084\n[0.052,0.115]",
                              "Public:0.122\n[0.091,0.153]",
                              "Public:0.041\n[0.009,0.074]",
                              "Public:0.125\n[0.094,0.156]"),
                    labels2 = c("CCP:0.421\n[0.327,0.516]",
                              "CCP:0.351\n[0.259,0.444]",
                              "CCP:0.165\n[0.056,0.275]",
                              "CCP:0.458\n[0.368,0.549]"))

pdf("Figure2.pdf",width=10, height=8)
datatidyr_2 %>% 
  ggplot(weight = wcn2)+
  geom_density_ridges(aes(y = str_survey, 
                          x = value,color = paste(str_survey, party),    
                          fill = paste(str_survey, party),
                          linetype = paste(str_survey, party)),
                      alpha = .001,na.rm = FALSE,scale = 0.95)+
  facet_grid(. ~ values)+
  scale_fill_cyclical(breaks = c("0", "1"),
                      labels = c("Public","CCP Member"),
                      values = c("#377eb8","#e41a1c"),
                      name = "") +
  scale_color_cyclical(breaks = c("0", "1"),
                       labels = c("Public","CCP Member"),
                       values = c("#377eb8","#e41a1c"),
                       name = "") +
  scale_linetype_cyclical(breaks = c("0", "1"),
                          labels = c("Public","CCP Member"),
                          values = c(1,5),
                          name = "") +
  ylab("")+xlab("")+
  geom_text(data=dg_cfps,    mapping=aes(x=6,y=1.5,label=labels1,color="#377eb8"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cfps,    mapping=aes(x=6,y=1.8,label=labels2,color="#e41a1c"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cgss2010,mapping=aes(x=6,y=2.5,label=labels1,color="#377eb8"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cgss2010,mapping=aes(x=6,y=2.8,label=labels2,color="#e41a1c"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cgss2012,mapping=aes(x=6,y=3.5,label=labels1,color="#377eb8"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cgss2012,mapping=aes(x=6,y=3.8,label=labels2,color="#e41a1c"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cgss2013,mapping=aes(x=6,y=4.5,label=labels1,color="#377eb8"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cgss2013,mapping=aes(x=6,y=4.8,label=labels2,color="#e41a1c"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cgss2015,mapping=aes(x=6,y=5.5,label=labels1,color="#377eb8"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cgss2015,mapping=aes(x=6,y=5.8,label=labels2,color="#e41a1c"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_abs3,    mapping=aes(x=6,y=6.5,label=labels1,color="#377eb8"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_abs3,    mapping=aes(x=6,y=6.8,label=labels2,color="#e41a1c"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_abs4,    mapping=aes(x=6,y=7.5,label=labels1,color="#377eb8"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_abs4,    mapping=aes(x=6,y=7.8,label=labels2,color="#e41a1c"),size=2.8,lineheight=0.8,hjust = 1)+
  theme_bw() + scale_x_continuous(expand=c(0.01,0))+
  scale_y_discrete(expand=c(0.01,0),
                   limits=c("CFPS2014","CGSS2010","CGSS2012",
                            "CGSS2013","CGSS2015",
                            "ABS3(2011)","ABS4(2015)"))+
  theme(text=element_text(family="Times"),
        legend.position="bottom",legend.direction="horizontal",
        axis.title.x=element_text(face="bold",vjust=-.5),
        axis.title.y=element_text(face="bold",vjust=1),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13))

dev.off()  
```

###################################################
# Figure 3: Citizen-Party Member-Cadre Comparison #
###################################################

```{r}
data_3 <- read_dta("ji_and_jiang_2019/data.dta")
data_3 = data_3[complete.cases(data$cate),]

datatidyr_3 <- data_3 %>% 
  gather(attribute, value, social_value:modern_all_value) %>% 
  mutate(values = factor(attribute, levels = c("social_value", "political_value", "intl_value", "modern_all_value"), 
                         labels = c("Social", "Political", "International", "Overall modern value")))

pdf("Figure3.pdf",width=10, height=8)

datatidyr_3 %>% ggplot(weight = wcn2) + 
  geom_density_ridges(aes(y = values, 
                          x = value, 
                          color = paste(values, cate),
                          linetype = paste(values, cate),
                          fill = paste(values, cate)), 
                      alpha = .001, na.rm = FALSE, scale=0.95) +
  scale_fill_cyclical(breaks = c("0", "1","2"),
                      labels = c("Public","CCP Member","Cadre"),
                      values = c("#377eb8","#e41a1c","#4daf4a"),
                      name = "") +
  scale_color_cyclical(breaks = c("0", "1","2"),
                       labels = c("Public","CCP Member","Cadre"),
                       values = c("#377eb8","#e41a1c","#4daf4a"),
                       name = "") +
  scale_linetype_cyclical(breaks = c("0", "1","2"),
                          labels = c("Public","CCP Member","Cadre"),
                          values = c(1,2,4),
                          name = "") +
  ylab("")+xlab("")+
  scale_y_discrete(expand=c(0.01,0),
                   limits=c("Overall modern value",
                            "International",
                            "Political",
                            "Social"))+
  annotate(geom="text", x=3, y=4.4,hjust = 0,size=4,
           color="#377eb8",lineheight=0.8,
           label="Public:0.011\n[0.004,0.018]")+
  annotate(geom="text", x=3, y=4.25,hjust = 0,size=4,
           color="#e41a1c",lineheight=0.8,
           label="Party:0.328\n[0.305,0.351]")+
  annotate(geom="text", x=3, y=4.1,hjust = 0,size=4,
           color="#4daf4a",lineheight=0.8,
           label="Cadre:0.563\n[0.508,0.618]")+
  annotate(geom="text", x=3, y=3.5,hjust = 0,size=4,
           color="#377eb8",lineheight=0.8,
           label="Public:0.122\n[0.091,0.153]")+
  annotate(geom="text", x=3, y=3.35,hjust = 0,size=4,
           color="#e41a1c",lineheight=0.8,
           label="Party:0.356\n[0.255,0.457]")+
  annotate(geom="text", x=3, y=3.2,hjust = 0,size=4,
           color="#4daf4a",lineheight=0.8,
           label="Cadre:0.317\n[0.116,0.518]")+
  annotate(geom="text", x=3, y=2.5,hjust = 0,size=4,
           color="#377eb8",lineheight=0.8,
           label="Public:0.041\n[0.009,0.074]")+
  annotate(geom="text", x=3, y=2.35,hjust = 0,size=4,
           color="#e41a1c",lineheight=0.8,
           label="Party:0.174\n[0.057,0.291]")+
  annotate(geom="text", x=3, y=2.2,hjust = 0,size=4,
           color="#4daf4a",lineheight=0.8,
           label="Cadre:0.100\n[-0.220,0.420]")+
  annotate(geom="text", x=3, y=1.5,hjust = 0,size=4,
           color="#377eb8",lineheight=0.8,
           label="Public:0.125\n[0.094,0.156]")+
  annotate(geom="text", x=3, y=1.35,hjust = 0,size=4,
           color="#e41a1c",lineheight=0.8,
           label="Party:0.465\n[0.366,0.564]")+
  annotate(geom="text", x=3, y=1.2,hjust = 0,size=4,
           color="#4daf4a",lineheight=0.8,
           label="Cadre:0.409\n[0.206,0.613]")+
  theme_bw()+theme(text=element_text(family="Times"),
                   legend.position="bottom",legend.direction="horizontal",
                   axis.title.x=element_text(face="bold",size=16,vjust=-.5),
                   axis.title.y=element_text(face="bold",size=16,vjust=1),
                   axis.text.x=element_text(size=12),
                   axis.text.y=element_text(size=14),
                   strip.text=element_text(size=13))
dev.off()
```


#####################################################################################
# Figure 4: Party-Public Comparison in Subsamples Less Affected Social Desirability #
#####################################################################################


```{r}
data_4 <- read_excel("ji_and_jiang_2019/Fig.xlsx", sheet = 4)

data_4 %>% mutate(Value = factor(Value, levels = c("social","political","intl","modern"),
                                 labels = c("Social","Political","International","Overall modern value")), 
                  question = factor(question, levels = c('Answer reliable.',
                                                         'No doubts about the survey.',
                                                         '"Government officials often violate law and abuse power"',
                                                         '"Officials often conceal information from the public"',
                                                         '"Criminal officials often escape punishment"'),
                                    labels = c('Answer reliable.', 
                                               'No doubts about the survey.',
                                               '"Government officials often \n violate law and abuse power"', 
                                               '"Officials often conceal \n information from the public"', 
                                               '"Criminal officials often \n escape punishment"'))
pd <- position_dodge(0.6)

pdf("Figure4.pdf",width=9, height=5)

ggplot(data_4, aes(x = question, y = mean,
                group = as.factor(party),
                shape = as.factor(party),
                color = as.factor(party),
                label = round(mean,3)))+
  geom_point(size = 1.5, position = pd)+
  geom_hline(aes(yintercept = 0), colour = "#62BCE9", linetype = "dashed")+
  geom_text(size = 2.8, hjust = 0.5, vjust = -0.6, position = pd, show.legend = FALSE)+
  geom_errorbar(aes(ymin = lb95, 
                    ymax = ub95), width = 0, position = pd)+
  facet_grid(. ~ Value)+
  scale_color_manual(values = c("#377eb8","#e41a1c"),
                     name = "",
                     breaks = c("0","1"),
                     labels = c("Public","CCP member"))+
  scale_shape_manual(name = "",
                     breaks = c("0","1"),
                     labels = c("Public","CCP member"),
                     values = c(19,17))+
  xlab("")+ylab("Weighted Mean Estimator")+
  scale_y_continuous(limits = c(-0.1,0.8), breaks = seq(-0,0.8,0.2))+
  theme_bw()+
  theme(text=element_text(family="Times"),
        legend.position="bottom",legend.direction="horizontal",
        axis.title.x=element_text(face="bold",size=16,vjust=-.5),
        axis.title.y=element_text(face="bold",size=16,vjust=1),
        axis.text.x = element_text(size=12),
        axis.text.y = element_text(hjust=0),
        axis.text.y.left  = element_text(size=10),
        strip.text=element_text(size=13),
        legend.text = element_text(size=10))+
  coord_flip()
dev.off() 



