---
title: "Untitled"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(haven)
library(readxl)
theme_set(theme_light())

full_data <- read_dta("ji_and_jiang_2019/data.dta")
read_dta("ji_and_jiang_2019/abs3_merge_party.dta")
read_dta("ji_and_jiang_2019/abs4_merge_party.dta")
```


######################################################################################
# Figure 1 Sample Deviation from Population Statistics: Before and After Reweighting #
######################################################################################


```{r}
data_1 <- read_excel("ji_and_jiang_2019/Fig.xlsx", sheet = 1)

datatidyr <- data_1 %>% gather(attribute, value, CCP:age) %>% 
  mutate(att = factor(attribute, levels = c("CCP", "female", "edu", "age"),
                      labels=c("% CCP membership","% of female CCP member","% of college educated CCP member","% of CCP member at age<=35"))) %>% 
  mutate(survey1 = factor(survey, levels = c("ABS4(2015)", "ABS3(2011)", "CGSS2015", "CGSS2013","CGSS2012","CGSS2010","CFPS2014")))

pdf("Figure1.pdf",width=10, height=4)

datatidyr %>% 
  ggplot(aes(x = value, y = att, group = as.factor(group),
                     shape = as.factor(group), color = as.factor(group))) + 
  geom_point(size = 2) + 
  facet_grid(. ~ survey1) + 
  scale_y_discrete(limits = c("% of CCP member at age<=35","% of college educated CCP member",
                            "% of female CCP member","% CCP membership")) +
  geom_vline(aes(xintercept=0), colour="#62BCE9", linetype="dashed") +
  scale_color_brewer(palette="Set1",
                     name = "",
                     breaks=c("Origin", "Raked"),
                     labels=c("Before weight calibration","After weight calibration")) +
  scale_shape_manual(name = "",
                     breaks=c("Origin", "Raked"),values=c(19,17),
                     labels=c("Before weight calibration","After weight calibration")) +
  xlab("% in Survey - % in Population")+ylab("")+
  scale_x_continuous(limits=c(-0.22,0.1),labels = scales::percent_format(accuracy = 1)) +
  theme_bw() + 
  theme(axis.text.x = element_text(size=8),
        axis.text.y = element_text(size=11),
        axis.title.x=element_text(face="bold",vjust=-.5,size=11),
        axis.title.y=element_text(face="bold",vjust=1),
        legend.text = element_text(size=11),
        strip.text=element_text(size=13),
        text=element_text(family="Times"),
        legend.position="bottom",
        legend.direction="horizontal")

```


#######################################################
# Figure 2: Main Result: Weighted Difference in Means #
#######################################################


```{r}
library(ggridges)

data_2 <- read_dta("ji_and_jiang_2019/data.dta")

datatidyr_2 <- data_2 %>% 
  gather(attribute, value, social_value:modern_all_value) %>% 
  mutate(values = factor(attribute, levels = c("social_value", "political_value", "intl_value", "modern_all_value"),
                         labels = c("Social","Political","International","Overall modern value")))

dg_cfps    <- data.frame(values = unique(datatidyr_2$values),
                         labels1 = c("Public:0.093\n[0.082,0.104]","","",""),
                         labels2 = c("CCP:0.410\n[0.373,0.447]","","",""))

dg_cgss2010 <- data.frame(values = unique(datatidyr_2$values),
                          labels1 = c("Public:-0.090\n[-0.109,-0.071]","","",""),
                          labels2 = c("CCP:0.337\n[0.287,0.386]","","",""))

dg_cgss2012 <- data.frame(values = unique(datatidyr_2$values),
                          labels1 = c("Public:-0.050\n[-0.069,-0.031]","","",""),
                          labels2 = c("CCP:0.412\n[0.360,0.463]","","",""))

dg_cgss2013 <- data.frame(values = unique(datatidyr_2$values),
                          labels1 = c("Public:-0.031\n[-0.050,-0.012]","","",""),
                          labels2 = c("CCP:0.301\n[0.243,0.360]","","",""))

dg_cgss2015 <- data.frame(values = unique(datatidyr_2$values),
                          labels1 = c("Public:-0.054\n[-0.074,-0.035]","","",""),
                          labels2 = c("CCP:0.287\n[0.229,0.345]","","",""))

dg_abs3 <- data.frame(values = unique(datatidyr_2$values),
                    labels1 = c("Public:0.012\n[-0.025,0.048]",
                              "Public:0.012\n[-0.025,0.048]",
                              "Public:0.005\n[-0.031,0.041]",
                              "Public:0.012\n[-0.024,0.048]"),
                    labels2 = c("CCP:0.230\n[0.150,0.310]",
                              "CCP:0.326\n[0.244,0.407]",
                              "CCP:0.169\n[0.084,0.254]",
                              "CCP:0.347\n[0.265,0.429]"))

dg_abs4 <- data.frame(values = unique(datatidyr_2$values),
                    labels1 = c("Public:0.084\n[0.052,0.115]",
                              "Public:0.122\n[0.091,0.153]",
                              "Public:0.041\n[0.009,0.074]",
                              "Public:0.125\n[0.094,0.156]"),
                    labels2 = c("CCP:0.421\n[0.327,0.516]",
                              "CCP:0.351\n[0.259,0.444]",
                              "CCP:0.165\n[0.056,0.275]",
                              "CCP:0.458\n[0.368,0.549]"))

pdf("Figure2.pdf",width=10, height=8)

datatidyr_2 %>% 
  ggplot(weight = wcn2)+
  geom_density_ridges(aes(y = str_survey, 
                          x = value,color = paste(str_survey, party),    
                          fill = paste(str_survey, party),
                          linetype = paste(str_survey, party)),
                      alpha = .001,na.rm = FALSE,scale = 0.95)+
  facet_grid(. ~ values)+
  scale_fill_cyclical(breaks = c("0", "1"),
                      labels = c("Public","CCP Member"),
                      values = c("#377eb8","#e41a1c"),
                      name = "") +
  scale_color_cyclical(breaks = c("0", "1"),
                       labels = c("Public","CCP Member"),
                       values = c("#377eb8","#e41a1c"),
                       name = "") +
  scale_linetype_cyclical(breaks = c("0", "1"),
                          labels = c("Public","CCP Member"),
                          values = c(1,5),
                          name = "") +
  ylab("")+xlab("")+
  geom_text(data=dg_cfps,    mapping=aes(x=6,y=1.5,label=labels1,color="#377eb8"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cfps,    mapping=aes(x=6,y=1.8,label=labels2,color="#e41a1c"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cgss2010,mapping=aes(x=6,y=2.5,label=labels1,color="#377eb8"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cgss2010,mapping=aes(x=6,y=2.8,label=labels2,color="#e41a1c"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cgss2012,mapping=aes(x=6,y=3.5,label=labels1,color="#377eb8"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cgss2012,mapping=aes(x=6,y=3.8,label=labels2,color="#e41a1c"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cgss2013,mapping=aes(x=6,y=4.5,label=labels1,color="#377eb8"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cgss2013,mapping=aes(x=6,y=4.8,label=labels2,color="#e41a1c"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cgss2015,mapping=aes(x=6,y=5.5,label=labels1,color="#377eb8"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_cgss2015,mapping=aes(x=6,y=5.8,label=labels2,color="#e41a1c"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_abs3,    mapping=aes(x=6,y=6.5,label=labels1,color="#377eb8"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_abs3,    mapping=aes(x=6,y=6.8,label=labels2,color="#e41a1c"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_abs4,    mapping=aes(x=6,y=7.5,label=labels1,color="#377eb8"),size=2.8,lineheight=0.8,hjust = 1)+
  geom_text(data=dg_abs4,    mapping=aes(x=6,y=7.8,label=labels2,color="#e41a1c"),size=2.8,lineheight=0.8,hjust = 1)+
  theme_bw() + scale_x_continuous(expand=c(0.01,0))+
  scale_y_discrete(expand=c(0.01,0),
                   limits=c("CFPS2014","CGSS2010","CGSS2012",
                            "CGSS2013","CGSS2015",
                            "ABS3(2011)","ABS4(2015)"))+
  theme(text=element_text(family="Times"),
        legend.position="bottom",legend.direction="horizontal",
        axis.title.x=element_text(face="bold",vjust=-.5),
        axis.title.y=element_text(face="bold",vjust=1),
        axis.text.x=element_text(size=12),
        strip.text=element_text(size=13))
```


###################################################
# Figure 3: Citizen-Party Member-Cadre Comparison #
###################################################


```{r}
data_3 <- read_dta("ji_and_jiang_2019/data.dta")
data_3 = data_3[complete.cases(data_3$cate),]

datatidyr_3 <- data_3 %>% 
  gather(attribute, value, social_value:modern_all_value) %>% 
  mutate(values = factor(attribute, levels = c("social_value", "political_value", "intl_value", "modern_all_value"), 
                         labels = c("Social", "Political", "International", "Overall modern value")))

pdf("Figure3.pdf",width=10, height=8)

datatidyr_3 %>% ggplot(weight = wcn2) + 
  geom_density_ridges(aes(y = values, 
                          x = value, 
                          color = paste(values, cate),
                          linetype = paste(values, cate),
                          fill = paste(values, cate)), 
                      alpha = .001, na.rm = FALSE, scale=0.95) +
  scale_fill_cyclical(breaks = c("0", "1","2"),
                      labels = c("Public","CCP Member","Cadre"),
                      values = c("#377eb8","#e41a1c","#4daf4a"),
                      name = "") +
  scale_color_cyclical(breaks = c("0", "1","2"),
                       labels = c("Public","CCP Member","Cadre"),
                       values = c("#377eb8","#e41a1c","#4daf4a"),
                       name = "") +
  scale_linetype_cyclical(breaks = c("0", "1","2"),
                          labels = c("Public","CCP Member","Cadre"),
                          values = c(1,2,4),
                          name = "") +
  ylab("")+xlab("")+
  scale_y_discrete(expand=c(0.01,0),
                   limits=c("Overall modern value",
                            "International",
                            "Political",
                            "Social"))+
  annotate(geom="text", x=3, y=4.4,hjust = 0,size=4,
           color="#377eb8",lineheight=0.8,
           label="Public:0.011\n[0.004,0.018]")+
  annotate(geom="text", x=3, y=4.25,hjust = 0,size=4,
           color="#e41a1c",lineheight=0.8,
           label="Party:0.328\n[0.305,0.351]")+
  annotate(geom="text", x=3, y=4.1,hjust = 0,size=4,
           color="#4daf4a",lineheight=0.8,
           label="Cadre:0.563\n[0.508,0.618]")+
  annotate(geom="text", x=3, y=3.5,hjust = 0,size=4,
           color="#377eb8",lineheight=0.8,
           label="Public:0.122\n[0.091,0.153]")+
  annotate(geom="text", x=3, y=3.35,hjust = 0,size=4,
           color="#e41a1c",lineheight=0.8,
           label="Party:0.356\n[0.255,0.457]")+
  annotate(geom="text", x=3, y=3.2,hjust = 0,size=4,
           color="#4daf4a",lineheight=0.8,
           label="Cadre:0.317\n[0.116,0.518]")+
  annotate(geom="text", x=3, y=2.5,hjust = 0,size=4,
           color="#377eb8",lineheight=0.8,
           label="Public:0.041\n[0.009,0.074]")+
  annotate(geom="text", x=3, y=2.35,hjust = 0,size=4,
           color="#e41a1c",lineheight=0.8,
           label="Party:0.174\n[0.057,0.291]")+
  annotate(geom="text", x=3, y=2.2,hjust = 0,size=4,
           color="#4daf4a",lineheight=0.8,
           label="Cadre:0.100\n[-0.220,0.420]")+
  annotate(geom="text", x=3, y=1.5,hjust = 0,size=4,
           color="#377eb8",lineheight=0.8,
           label="Public:0.125\n[0.094,0.156]")+
  annotate(geom="text", x=3, y=1.35,hjust = 0,size=4,
           color="#e41a1c",lineheight=0.8,
           label="Party:0.465\n[0.366,0.564]")+
  annotate(geom="text", x=3, y=1.2,hjust = 0,size=4,
           color="#4daf4a",lineheight=0.8,
           label="Cadre:0.409\n[0.206,0.613]")+
  theme_bw()+theme(text=element_text(family="Times"),
                   legend.position="bottom",legend.direction="horizontal",
                   axis.title.x=element_text(face="bold",size=16,vjust=-.5),
                   axis.title.y=element_text(face="bold",size=16,vjust=1),
                   axis.text.x=element_text(size=12),
                   axis.text.y=element_text(size=14),
                   strip.text=element_text(size=13))
```


#####################################################################################
# Figure 4: Party-Public Comparison in Subsamples Less Affected Social Desirability #
#####################################################################################


```{r}
data_4 <- read_excel("ji_and_jiang_2019/Fig.xlsx", sheet = 4)

data_4 %>% mutate(Value = factor(Value, levels = c("social","political","intl","modern"),
                                 labels = c("Social","Political","International","Overall modern value")), 
                  question = factor(question, levels = c('Answer reliable.',
                                                         'No doubts about the survey.',
                                                         '"Government officials often violate law and abuse power"',
                                                         '"Officials often conceal information from the public"',
                                                         '"Criminal officials often escape punishment"'),
                                    labels = c('Answer reliable.', 
                                               'No doubts about the survey.',
                                               '"Government officials often \n violate law and abuse power"', 
                                               '"Officials often conceal \n information from the public"', 
                                               '"Criminal officials often \n escape punishment"')))
pd <- position_dodge(0.6)

pdf("Figure4.pdf",width=9, height=5)

ggplot(data_4, aes(x = question, y = mean,
                group = as.factor(party),
                shape = as.factor(party),
                color = as.factor(party),
                label = round(mean,3)))+
  geom_point(size = 1.5, position = pd)+
  geom_hline(aes(yintercept = 0), colour = "#62BCE9", linetype = "dashed")+
  geom_text(size = 2.8, hjust = 0.5, vjust = -0.6, position = pd, show.legend = FALSE)+
  geom_errorbar(aes(ymin = lb95, 
                    ymax = ub95), width = 0, position = pd)+
  facet_grid(. ~ Value)+
  scale_color_manual(values = c("#377eb8","#e41a1c"),
                     name = "",
                     breaks = c("0","1"),
                     labels = c("Public","CCP member"))+
  scale_shape_manual(name = "",
                     breaks = c("0","1"),
                     labels = c("Public","CCP member"),
                     values = c(19,17))+
  xlab("")+ylab("Weighted Mean Estimator")+
  scale_y_continuous(limits = c(-0.1,0.8), breaks = seq(-0,0.8,0.2))+
  theme_bw()+
  theme(text=element_text(family="Times"),
        legend.position="bottom",legend.direction="horizontal",
        axis.title.x=element_text(face="bold",size=16,vjust=-.5),
        axis.title.y=element_text(face="bold",size=16,vjust=1),
        axis.text.x = element_text(size=12),
        axis.text.y = element_text(hjust=0),
        axis.text.y.left  = element_text(size=10),
        strip.text=element_text(size=13),
        legend.text = element_text(size=10))+
  coord_flip()
```


########################################
# Figure 5: Heterogenous Party Effects #
########################################


```{r}
data_5 <- read_excel("ji_and_jiang_2019/Fig.xlsx", sheet = 5)

data_5$Value <- factor(data_5$Value, levels = c("social", "political", "intl", "modern"),labels=c("Social","Political","International","Overall modern value"))

pd <- position_dodge(0.8)

pdf("Figure5.pdf", width=9, height=8)

ggplot(data_5,aes(x = cate, y = mean,label = round(mean,3),
                color = as.factor(party),shape = as.factor(party)))+
  geom_hline(aes(yintercept=0), colour="#62BCE9", linetype="dashed")+
  geom_point(size = 1.8, position = pd)+
  geom_errorbar(aes(ymin = lb95, ymax = ub95),width = 0, position = pd)+
  geom_text(size = 2.8, hjust = 0.5,vjust = -0.6,
            position = pd, show.legend=FALSE)+
  facet_grid(~ Value)+
  scale_y_continuous(limits = c(-0.6,1.02),breaks = seq(-0.4,1.0,0.4)) + 
  scale_x_discrete(limits = c("75%-100% (highest)",
                            "25%-75% (middle)",
                            "0%-25% (lowest)",
                            "Income level",
                            "Old (60)",
                            "Middle age (45)",
                            "Young (30)",
                            "Age",
                            "Urban",
                            "Rural",
                            "Residency",
                            "Female",
                            "Male",
                            "Gender",
                            "College",
                            "No college",
                            "Education")) + 
  scale_color_manual(values=c("#377eb8","#e41a1c"),
                     name = "",
                     breaks=c("0","1"),
                     labels=c("Public","CCP member"))+
  scale_shape_manual(name = "",
                     breaks=c("0","1"),
                     labels=c("Public","CCP member"),
                     values=c(19,17))+
  xlab("")+ylab("Predicted Ideology")+theme_bw() +
  theme(text=element_text(family="Times"),
        legend.position="bottom",
        legend.direction="horizontal",
        axis.title.x=element_text(face="bold",size=16,vjust=-.5),
        axis.title.y=element_text(face="bold",size=16,vjust=1),
        axis.text.x=element_text(size=12),
        axis.text.y = element_text(size=c(10,10,10,11,10,10,10,
                                11,10,10,11,10,10,11,10,10,11),
                      face = c('plain','plain','plain','bold',
                               'plain','plain','plain','bold',
                               'plain','plain','bold','plain',
                               'plain','bold','plain','plain',
                               'bold'),hjust = 0),
        strip.text.x = element_text(size=13),
        legend.text = element_text(size=11))+
  coord_flip()

```


####################################
# Figure A.1: PCA and Cronbach??s ?? #
####################################


```{r}
data_6 <- read_excel("ji_and_jiang_2019/Fig.xlsx", sheet = 6)

data_6 <- subset(data_6,data_6$comp<11)

data_6$Value <- factor(data_6$Value, levels = c("social", "political",
                                         "intl", "modern"),
                    labels=c("Social","Political","International","Overall modern value"))
data_6$survey <- factor(data_6$survey, levels = c("ABS4(2015)", "ABS3(2011)", "CGSS2015", "CGSS2013","CGSS2012","CGSS2010","CFPS2014"))

pdf("Figurea1.pdf",width=10, height=8)

data_6 %>% 
  ggplot(aes(x=comp,y=pro,label=propt)) +
  geom_bar(stat="identity") + 
  geom_line() + 
  geom_point() +
  geom_text(vjust=-0.1,hjust=-0.1) +
  geom_text(data=data,mapping=aes(x=9,y=0.5,label=alpha),
            size=4,lineheight=0.8,hjust = 1,parse = TRUE) +
  facet_grid(survey ~ Value) +
  scale_x_continuous(limits=c(0.5,10.5),breaks=seq(1,10,1))+
  scale_y_continuous(limits=c(0,0.64))+
  ylab("Explained variances share")+xlab("Component Number")+
  theme_bw() + 
  theme(text=element_text(family="Times"),
                   legend.position="bottom",
                   legend.direction="horizontal",
                   axis.title.x=element_text(face="bold",vjust=-.5),
                   axis.title.y=element_text(face="bold",vjust=1),
                   title=element_text(face="bold",size=16,vjust=1.5),
                   axis.text.x=element_text(size=12),
                   strip.text=element_text(size=13))

```


############################################################################
# FFigure A.3: Comparing Demographics of CCP Members and Population Census #
############################################################################


```{r}
data_7 <- read_excel("ji_and_jiang_2019/Fig.xlsx", sheet = 7)

data_7_tidied <- data_7 %>% gather(census, value, "Population Census": "CCP Census")

theme_set(theme_bw() + 
            theme(text = element_text(family="Times"),
                  legend.position = "bottom", 
                  legend.direction = "horizontal", 
                  axis.title.x = element_text(face="bold",vjust=-.5),
                  axis.title.y = element_text(face="bold",vjust=1),
                  title = element_text(face="bold",size=16,vjust=1.5),
                  axis.text.x=element_text(size=12),
                  strip.text=element_text(size=13)))

pdf("Figurea3.pdf",width=6, height=8)

ggplot(data_7_tidied, aes(x=att, y=value,fill=census))+
  geom_bar(stat = "identity",position="dodge", 
           colour="black",alpha=0.5)+
  scale_fill_brewer(palette="Set1",name = "",
                    breaks=c("CCP Census", "Population Census"),
                    labels=c("CCP Census", "Population Census"))+
  scale_x_discrete(limits=c("minority","some university and above",
                            "71 and above","66-70","61-65",
                            "56-60","51-55","46-50","41-45",
                            "36-40","31-35","18-30","female"))+
  xlab("Attribute")+ylab("Proportion")+
  coord_flip()

```


##################################################################################################
# Figure A.6: Correlations between Social and Political Domains for Party Members and NonMembers #
##################################################################################################

```{r}
library(gridExtra)

data_8 <- read_dta("ji_and_jiang_2019/data.dta")

party <- subset(data_8, data_8$party==1)
public <- subset(data_8, data_8$party==0)

p1<-ggplot(party,aes(x=social_value,y=political_value))+
  geom_point(alpha=0.7)+geom_smooth(method='lm')+
  xlab("Social")+ylab("Political")+
  annotate(geom="text", x=-4, y=4,hjust = 0,size=5,
           label  = "paste(Party: rho==0.467, \" *** \")",
           parse = TRUE)+
  scale_x_continuous(limits=c(-4.1,4.1),breaks=seq(-4,4,1))+
  scale_y_continuous(limits=c(-4.1,4.1),breaks=seq(-4,4,1))

p2<-ggplot(public,aes(x=social_value,y=political_value))+
  geom_point(alpha=0.7)+geom_smooth(method='lm')+
  xlab("Social")+ylab("")+
  annotate(geom="text", x=-4, y=4,hjust = 0,size=5,
           label  = "paste(Public: rho==0.492, \" *** \")",
           parse = TRUE)+
  scale_x_continuous(limits=c(-4.1,4.1),breaks=seq(-4,4,1))+
  scale_y_continuous(limits=c(-4.1,4.1),breaks=seq(-4,4,1))

pdf("Figurea6.pdf", width=10, height=5)
grid.arrange(p1,p2, ncol=2, nrow=1)

```


###########################################
# Figure A.7: By Year of Party Enrollment #
###########################################

```{r}

data_10 <- read_excel("ji_and_jiang_2019/Fig.xlsx", sheet = 10)

data_10_tidied <- data_10 %>% gather(attribute, value, social:modern)

theme_set(theme_bw() + 
            theme(text=element_text(family="Times"),
                  legend.position="bottom",
                  legend.direction="horizontal",
                  axis.title.x=element_text(face="bold",vjust=-.5),
                  axis.title.y=element_text(face="bold",vjust=1),
                  title=element_text(face="bold",size=16,vjust=1.5),
                  axis.text.x=element_text(size=12),
                  axis.text.y=element_text(size=12),
                  strip.text=element_text(size=13)))

ggplot(data_10_tidied,aes(x = yrgroup, 
                          y = value, 
                          group = attribute, 
                          shape = attribute)) +
  geom_point(size = 2) +
  geom_line(aes(linetype = attribute)) +
  scale_linetype_manual(name = "",
                        breaks = c("social", 
                                   "political", 
                                   "intl", 
                                   "modern"),
                        labels = c("Social",
                                   "Political",
                                   "International",
                                   "Overall modern value"),
                        values = c("dashed",
                                   "twodash",
                                   "solid",
                                   "dotted")) +
  scale_shape_manual(name = "",
                     breaks = c("social", 
                                "political",
                                "intl",
                                "modern"),
                     labels = c("Social",
                                "Political",
                                "International",
                                "Overall modern value"),
                     values = c(19,17,18,15)) +
  xlab("Year Group")+ylab("")+
  theme(legend.text = element_text(size=11))+
  scale_x_discrete(limits=c("<1950","1950-1965","1966-1976",
                            "1977-1989","1990-2002",
                            "2003-2012",">2012"))

```

```{r}
