---
title: "Untitled"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
library(scales)
library(readxl)
library(viridis)
theme_set(theme_light())

# read in and clean data
mcf_docs_raw <- read_excel("MCF_docs.xlsx") %>% 
  mutate(date = str_remove(date, "（通過）")) %>% 
  mutate(date = ymd(date)) %>% 
  mutate(date_year = year(date)) %>%
  mutate(entity = str_trim(entity)) %>% 
  mutate(entity_rank = as.character(entity_rank))

mcf_0213_raw <- read_excel("MCF_docs.xlsx", sheet = 3) %>% 
  mutate(date = ymd(date)) %>% 
  mutate(date_year = year(date)) %>%
  mutate(entity = str_trim(entity))
```

## MC by number over time 

```{r}
mcf_docs_raw %>% 
  distinct(index, .keep_all = T) %>% 
  filter(date_year < 2021) %>% 
  count(date_year) %>% 
  ggplot(aes(date_year, n)) +
  geom_point(size = 2) +
  geom_line(size = 1) + 
  # geom_vline(xintercept = 2017) +
  scale_x_continuous(breaks = seq(2013, 2020, 1)) +
  scale_y_continuous(breaks = seq(0, 40, 5)) +
  labs(title = "Figure 2. Number of Policy Documents relating to MCF over time (2013-2020)", 
       x = " ", 
       y = " ", 
       caption = "Data Source: MCF documents dataset ver.1") +
  theme_classic() +
  theme(plot.title = element_text(family = "Times", face = "bold", size = 15))

# Japanese
mcf_docs_raw %>% 
  distinct(index, .keep_all = T) %>% 
  filter(date_year < 2021) %>% 
  count(date_year) %>% 
  ggplot(aes(date_year, n)) +
  geom_line(size = 1) + 
  # geom_vline(xintercept = 2017) +
  scale_x_continuous(breaks = seq(2013, 2020, 1)) +
  scale_y_continuous(breaks = seq(0, 40, 5)) +
  labs(title = "図2. 「軍民融合」に関する政策文書の公布件数の推移 (2013-2020)", 
       x = " ", 
       y = " ", 
       caption = "Data Source: MCF documents dataset ver.1") +
  theme_classic(base_family = "HiraKakuProN-W6")
```

## Plot MCF by document type for the entire period (without issuing authority)

```{r}
mcf_docs_raw %>% 
  distinct(index, .keep_all = TRUE) %>% 
  count(type, sort = T) %>% 
  mutate(type = fct_reorder(type, n)) %>% 
  ggplot(aes(n, type)) +
  geom_col() +
  labs(title = "Figure 5. MCF policy documents by type (2013-2020)", 
       y = " ",
       x = "Number of documents", 
       fill = " ", 
       caption = "Data Source: MCF Documents Dataset Ver. 1") +
  theme_classic() +
  theme(axis.text.y = element_text(family = "Songti TC"), 
        plot.title = element_text(family = "Times", face = "bold", size = 15))

# Japanese
mcf_docs_raw %>% 
  distinct(index, .keep_all = TRUE) %>% 
  count(type, sort = T) %>% 
  mutate(type = fct_recode(type, 
                           "意見" = "意见", 
                           "目録" = "目录", 
                           "弁法" = "办法", 
                           "規画" = "规划", 
                           "計画" = "计划", 
                           "暫定弁法" = "暂行办法", 
                           "規則" = "规则",
                           "規定" = "规定", 
                           "細則" = "细则", 
                           "挙措" = "举措", 
                           "規範体系" = "规范体系", 
                           "綱要" = "纲要", 
                           "大綱" = "大纲"),
         type = fct_reorder(type, n)) %>% 
  ggplot(aes(n, type)) +
  geom_col() +
  labs(title = "図6. 「軍民融合」に関する政策文書の種類別件数 (2013-2020)", 
       y = " ",
       x = "公布文書の件数", 
       fill = " ", 
       caption = "Data Source: MCF Documents Dataset Ver. 1") +
  theme_classic(base_family = "HiraKakuProN-W6")
```

## Plot MCF by document type (with issuing authority)

```{r}
mcf_docs_raw %>% 
  count(type, entity_rank) %>% 
  mutate(entity_rank = fct_recode(entity_rank, 
                                  "core leaders" = "1", 
                                  "staff & leadership groups" = "2", 
                                  "commissions & super ministries" = "3", 
                                  "line ministries" = "4", 
                                  "ministerial bureaus" = "5")) %>% 
  mutate(type = fct_recode(type, 
                           "意見" = "意见", 
                           "目録" = "目录", 
                           "弁法" = "办法", 
                           "規画" = "规划", 
                           "計画" = "计划", 
                           "暫定弁法" = "暂行办法", 
                           "規則" = "规则",
                           "規定" = "规定", 
                           "細則" = "细则", 
                           "挙措" = "举措", 
                           "規範体系" = "规范体系", 
                           "綱要" = "纲要", 
                           "大綱" = "大纲"), 
         type = fct_reorder(type, n, sum)) %>% 
  ggplot(aes(n, type, fill = entity_rank)) +
  geom_col() +
  labs(title = "Figure 5. MCF policy documents by type (2013-2020)", 
       y = "",
       x = "Number of Documents", 
       fill = " ", 
       caption = "Data Source: MCF Documents Dataset Ver. 1") +
  scale_fill_viridis(discrete = TRUE, option = "B") + 
  theme_classic(base_family = "HiraKakuProN-W6") +
  theme(plot.title = element_text(face = "bold", size = 12), 
        legend.position = "bottom")

# Japanese
mcf_docs_raw %>% 
  count(type, entity_rank) %>% 
  mutate(entity_rank = fct_recode(entity_rank, 
                                  "党指導部" = "1", 
                                  "党中央機構・領導小組" = "2", 
                                  "政府委員会・統括省（部）" = "3", 
                                  "管轄省（部）" = "4", 
                                  "管轄庁（局）" = "5")) %>% 
  mutate(type = fct_recode(type, 
                           "意見" = "意见", 
                           "目録" = "目录", 
                           "弁法" = "办法", 
                           "規画" = "规划", 
                           "計画" = "计划", 
                           "暫定弁法" = "暂行办法", 
                           "規則" = "规则",
                           "規定" = "规定", 
                           "細則" = "细则", 
                           "挙措" = "举措", 
                           "規範体系" = "规范体系", 
                           "綱要" = "纲要", 
                           "大綱" = "大纲"), 
         type = fct_reorder(type, n, sum)) %>% 
  ggplot(aes(n, type, fill = entity_rank)) +
  geom_col() +
  labs(title = "図6. 「軍民融合」に関する政策文書の種類別件数 (2013-2020)", 
       y = "",
       x = "公布文書の件数", 
       fill = " ", 
       caption = "Data Source: MCF Documents Dataset Ver. 1") +
  scale_fill_viridis(discrete = TRUE, option = "B") + 
  theme_classic(base_family = "HiraKakuProN-W6") +
  theme(plot.title = element_text(face = "bold", size = 12), 
        legend.position = "bottom")
  # theme_bw(base_family = "Songti TC")
  
```

## MCF by document type over time

```{r}
# Plot MCF by type over time
mcf_docs_raw %>% 
  distinct(index, .keep_all = T) %>% 
  mutate(type = fct_lump(type, 6)) %>%
  filter(date_year < 2021) %>% 
  count(date_year, type) %>% 
  ggplot(aes(date_year, n, fill = type)) +
  geom_col() + 
  scale_x_continuous(breaks = seq(2013, 2020, 1)) +
  scale_fill_viridis(discrete = TRUE, option = "B") +
  labs(title = "Figure 6. MCF policy documents by type over time", 
       x = " ",
       y = "Number of documents", 
       fill = " ") +
  theme_classic() +
  theme(legend.text = element_text(family = "Songti TC"),
        plot.title = element_text(face = "bold")) 
```

## MCF by issuing entity for the entire period

```{r}
mcf_docs_raw %>% 
  count(entity, sort = T) %>% 
  filter(n > 1) %>% 
  mutate(entity = fct_reorder(entity, n)) %>% 
  ggplot(aes(n, entity)) +
  geom_col() +
  labs(title = "Figure 2. MCF policy documents by entity of issuance", 
       y = " ",
       x = "Number of documents", 
       fill = " ", 
       caption = "Data Source: MCF Documents Dataset Ver.1") +
  theme_classic() +
  theme(axis.text.y = element_text(family = "Songti TC"), 
        plot.title = element_text(face = "bold"))
```

## MCF by issuing entity over time 

```{r}
# Plot MCF documents by entity over time
mcf_docs_raw %>% 
  distinct(index, .keep_all = T) %>% 
  mutate(entity = fct_lump(entity, 6),
         entity = fct_relevel(entity, 
                              "中央军民融合发展委员会", 
                              "国务院", 
                              "财政部", 
                              "工业和信息化部", 
                              "国防科技工业局")) %>%
  filter(date_year < 2021) %>% 
  count(date_year, entity) %>% 
  ggplot(aes(date_year, n, fill = entity)) +
  geom_col() + 
  scale_x_continuous(breaks = seq(2013, 2020, 1)) +
  labs(title = "Figure 3. MCF policy documents by issuing entity over time (2013-2020)", 
       x = " ",
       y = "Number of documents", 
       fill = " ", 
       caption = "Data Source: MCF Documents Dataset Ver.1") +
  scale_fill_viridis(discrete = TRUE, option = "B") +
  theme_classic() +
  theme(legend.text = element_text(family = "Songti TC"),
        plot.title = element_text(face = "bold")) 

# Japanese
mcf_docs_raw %>% 
  distinct(index, .keep_all = T) %>% 
  mutate(entity = fct_lump(entity, 6),
         entity = fct_recode(entity, 
                             "中央軍民融合発展委員会" = "中央军民融合发展委员会", 
                             "国務院" = "国务院",
                             "財政部" = "财政部", 
                             "工業情報化省" = "工业和信息化部", 
                             "国防科技工業局" = "国防科技工业局", 
                             "中央軍委装備発展部" = "中央军委装备发展部", 
                             "その他" = "Other"), 
         entity = fct_relevel(entity, 
                              "中央軍民融合発展委員会", 
                              "国務院", 
                              "財政部", 
                              "工業情報化省", 
                              "国防科技工業局")) %>%
  filter(date_year < 2021) %>% 
  count(date_year, entity) %>% 
  ggplot(aes(date_year, n, fill = entity)) +
  geom_col() + 
  scale_x_continuous(breaks = seq(2013, 2020, 1)) +
  labs(title = "図3. 公布機関別に見た「軍民融合」に関する政策文書の件数推移 (2013-2020)", 
       x = " ",
       y = "文書の件数", 
       fill = " ", 
       caption = "Data Source: MCF Documents Dataset Ver.1") +
  scale_fill_viridis(discrete = TRUE, option = "B") +
  theme_classic(base_family = "HiraKakuProN-W6") +
  theme(plot.title = element_text(face = "bold"), 
        legend.position = "bottom") 
```



```{r}
# English name
mcf_docs_raw %>% 
  mutate(entity = fct_recode(entity, "SASTIND" = "国防科技工业局", 
                             "MIIT" = "工业和信息化部", 
                             "NDRC" = "国家发展和改革委", 
                             "MSC" = "科技部", 
                             "CCMCFD" = "中央军民融合发展委员会", 
                             "MOF" = "财政部", 
                             "CMCEDD" = "中央军委装备发展部", 
                             "SC" = "国务院", 
                             "CMC" = "中央军委", 
                             "CNIPA" = "国家知识产权局", 
                             "GAD" = "总装备部", 
                             "CC" = "中共中央", 
                             "MOE" = "教育部", 
                             "CSRC" = "中国证券监督管理委", 
                             "CMCSTC" = "中央军委科技委", 
                             "SAC" = "国家标准化管理委员会")) %>% 
  count(entity, sort = T)
```

## Network Analysis 

```{r}
library(widyr)
library(reshape2)

correlations <- mcf_docs_raw %>% 
  pairwise_cor(entity, index, sort = T)

correlations_1316 <- mcf_docs_raw %>% 
  filter(date_year < 2017)  %>% 
  pairwise_cor(entity, index, sort = T)

correlations_1720 <- mcf_docs_raw %>% 
  filter(date_year > 2016)  %>% 
  pairwise_cor(entity, index, sort = T)

```

## Correlation among agencies over MCF

```{r}
# what tends to appear with SASTIND?
correlations %>% 
  filter(item1 == "国防科技工业局") %>% 
  mutate(item2 = fct_reorder(item2, correlation)) %>% 
  ggplot(aes(item2, correlation)) +
  geom_col() +
  coord_flip() +
  labs(title = "Who tends to work with SASTIND?", 
       subtitle = "Among the entities that issued at least 2 policy documents") +
  theme_bw(base_family = "Songti TC")

correlations %>% 
  filter(item1 == "工业和信息化部") %>% 
  mutate(item2 = fct_reorder(item2, correlation)) %>% 
  ggplot(aes(item2, correlation)) +
  geom_col() +
  coord_flip() +
  labs(title = "Who tends to work with MIIT?", 
       subtitle = "Among the entities that issued at least 2 policy documents") +
  theme_bw(base_family = "Songti TC")

correlations %>% 
  filter(item1 == "国家发展和改革委") %>% 
  mutate(item2 = fct_reorder(item2, correlation)) %>% 
  ggplot(aes(item2, correlation)) +
  geom_col() +
  coord_flip() +
  labs(title = "Who tends to work with NDRC?", 
       subtitle = "Among the entities that issued at least 2 policy documents") +
  theme_bw(base_family = "Songti TC")
```

## MCF policy network

```{r}
library(ggraph)
library(igraph)
library(gridExtra)
library(cowplot)

g <- correlations %>% 
  graph_from_data_frame(directed = FALSE) 

network_plot <- function(data) {
  data %>% 
  filter(correlation > 0) %>% 
  graph_from_data_frame() %>% 
  ggraph(layout = "with_kk") +
  geom_edge_link(aes(alpha = correlation)) +
  geom_node_point() +
  geom_node_text(aes(label = name), family = "Songti TC", repel = TRUE) +
  theme(plot.title = element_text(face = "bold", size = 15))
}

correlations %>% 
  network_plot() +
  labs(title = "Figure 4. The structure of MCF policy network", 
       caption = "Data Source: MCF Documents Dataset Ver.1") 

network_plot_1316 <- correlations_1316 %>% 
  network_plot() +
  labs(title = "Figure 4. Central MCF policy network between 2013 and 2016") +
  theme(legend.position = "bottom") 

# Japanese
correlations_1316 %>% 
  network_plot() +
  labs(title = "図4. 中央における「軍民融合」政策ネットワーク（2013-2016)") +
  theme(plot.title = element_text(family = "HiraKakuProN-W6", size = 12), 
        legend.position = "none") 

network_plot_1720 <- correlations_1720 %>% 
  network_plot() + 
  labs(title = "Figure 5. Central MCF policy network between 2017 and 2020") +
  theme(legend.position = "bottom")

# Japanese
correlations_1720 %>% 
  network_plot() +
  labs(title = "図5. 中央における「軍民融合」政策ネットワーク（2017-2020)") +
  theme(plot.title = element_text(family = "HiraKakuProN-W6", size = 12), 
        legend.position = "none") 

title_gg <- ggdraw() + draw_label("Figure 4. The structure of MCF policy network (before and after 2017)", 
             size = 15, fontface = "bold", hjust = .51)

gridded <- plot_grid(network_plot_1316, network_plot_1720, nrow = 2)

plot_grid(title_gg, gridded, ncol = 1, rel_heights = c(0.05, 1))
```

## MCF documents by domain

```{r}
mcf_docs_raw %>% 
  distinct(index, .keep_all = T) %>% 
  mutate(date_year = year(date), 
         domain = fct_recode(domain, 
                             "industry" = "产业", 
                             "infrastucture" = "基础", 
                             "science & technology" = "科技", 
                             "education" = "教育资源", 
                             "social service" = "社会服务"), 
         domain = fct_relevel(domain, 
                              "industry", 
                              "infrastructure", 
                              "science & technology",
                              "education", 
                              "social service")) %>% 
  filter(date_year < 2021) %>% 
  count(domain, date_year)  %>% 
  filter(domain != "原则") %>% 
  ggplot(aes(date_year, n, fill = domain)) +
  geom_col() + 
  scale_x_continuous(breaks = seq(2013, 2020, 1)) +
  labs(title = "Figure 7. MCF policy documents by domain over time (2013-2020)", 
       x = " ",
       y = "Number of documents", 
       fill = " ", 
       caption = "Data Source: MCF Documents Dataset Ver.1") +
  scale_fill_grey() +
  #scale_fill_viridis(discrete = TRUE, option = "B") +
  theme_classic() +
  theme(legend.text = element_text(family = "Songti TC", size = 11),
        legend.position = "bottom",
        plot.title = element_text(face = "bold", size = 15)) 

# Japanese
mcf_docs_raw %>% 
  distinct(index, .keep_all = T) %>% 
  mutate(date_year = year(date), 
         domain = fct_recode(domain, 
                             "産業" = "产业", 
                             "基礎" = "基础", 
                             "科学技術" = "科技", 
                             "教育" = "教育资源", 
                             "社会サービス" = "社会服务"), 
         domain = fct_relevel(domain, 
                              "産業", 
                              "基礎", 
                              "科学技術",
                              "教育", 
                              "社会サービス")) %>% 
  filter(date_year < 2021) %>% 
  count(domain, date_year)  %>% 
  filter(domain != "原则") %>% 
  ggplot(aes(date_year, n, fill = domain)) +
  geom_col() + 
  scale_x_continuous(breaks = seq(2013, 2020, 1)) +
  labs(title = "図7. 領域別に見た「軍民融合」政策文書の件数推移 (2013-2020)", 
       x = " ",
       y = "文書の件数", 
       fill = " ", 
       caption = "Data Source: MCF Documents Dataset Ver.1") +
  scale_fill_grey() +
  #scale_fill_viridis(discrete = TRUE, option = "B") +
  theme_classic(base_family = "HiraKakuProN-W6") +
  theme(legend.position = "bottom",
        plot.title = element_text(face = "bold")) 
```

## MCF documents before 2013

```{r}
mcf_before_2013 <- mcf_0213_raw %>% 
  distinct(index, .keep_all = TRUE) %>% 
  filter(date_year < 2013, 
         date_year > 2002) %>% 
  select(title, entity, date, type, date_year)

mcf_after_2013 <- mcf_docs_raw %>% 
  distinct(index, .keep_all = TRUE) %>%
  filter(date_year < 2021) %>% 
  select(title, entity, date, type, date_year)

mcf_0220_selected <- bind_rows(mcf_before_2013, mcf_after_2013)

mcf_0220_selected %>% 
  count(date_year) %>% 
  ggplot(aes(date_year, n)) +
  geom_point(size = 2) +
  geom_line(size = 1) + 
  # geom_vline(xintercept = 2017) +
  scale_x_continuous(breaks = seq(2002, 2020, 1)) +
  scale_y_continuous(breaks = seq(0, 40, 5)) +
  labs(title = "Figure 2. Number of Policy Documents relating to MCF over time (2003-2020)", 
       x = " ", 
       y = " ", 
       caption = "Data Source: MCF documents dataset ver.1") +
  theme_classic() +
  theme(plot.title = element_text(family = "Times", face = "bold", size = 14))
ggsave(filename = "mcf-presentation/fig-2_number_of_policy_documents_over_time.pdf", width = 8, height = 5)
```


